### 2015-04-28 inst/examples/synchrony-example.Rmd
more time series plotting checks

>>>>

### Try with Idaho
```{r idaho_try, echo=TRUE}
site <- "Idaho"
spp_list <- sort(c("PSSP","HECO","POSE","ARTR"))
num_spp <- length(spp_list)
id_data <- data.frame(quad=NA, year=NA, totCover=NA, species=NA)
for(dospp in 1:num_spp){ #loop through species to read in data
  spp_now <- spp_list[dospp]
  quad_file <- paste("../../data/", site,"/",spp_now,"/quadratCover.csv",sep="")
  spp_data <- read.csv(quad_file)
  spp_data$species <- spp_now
  id_data <- rbind(id_data, spp_data)
} #end species looping for raw data
id_data <- id_data[2:nrow(id_data),] #remove first NA row
id_data <- subset(id_data, species!="ARTR") #take out the shrub

out <- get_comm_synchrony(ts_data = id_data)
str(out)
names(out)
```

### Plot Idaho per capita growth rates
```{r plotit_idaho, echo=TRUE, include=TRUE}
pgr_data <- out$growth_rates
pgr_melt <- melt(pgr_data, id.vars = "year")
ggplot(pgr_melt, aes(x=(year+1900), y=value, color=variable))+
  geom_line()+
  geom_point()
```

### Plot Idaho percent cover through time
```{r perc_cover, echo=TRUE, include=TRUE}
ggplot(out$percent_cover, aes(x=(year+1900), y=tot_cover, color=species))+
  geom_line()+
  geom_point()
```
